A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-10 deprecated.tex
Modify choice of data storage

>>>>

\subsection{choice of data storage}
We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible for data streams, and it is difficult to verify arbitrary data pieces, track data streams and categorize.

### 2020-06-10 paper.tex
Modify choice of data storage

% use IPFS as searching indexes
\subsection{Choice of Data Storage}
Data storage is an important element of data marketplace where the data assets are reserved. We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.

% MAM
MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control. With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.

In the IOTA protocol, \textbf{seed} is the identifier of its owner. An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle. With the seed, the owner can create addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.

>>>>

% use IPFS as searching indexes
\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. Also, on top of MAM, a self-soverign identity system is built to prove the participants' identities without any trusted authorities. Furthermore, MAM fulfills the requirements of scalability which reduce the number of keys and addresses that need to be managed by participants, and confidentiality that provides access control.

MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control. With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage. In the IOTA protocol, \textbf{seed} is the identifier of its owner. An IOTA seed represents the ownership of all things associated with the user in the IOTA ecosystem, such as IOTA tokens or messages on the Tangle. With the seed, the owner can create addresses and signatures in order to issue transactions or publish messages to MAM channels and endpoints.
